\section*{}
\begin{center}
  \centerline{\textsc{\LARGE  Graph Convolutional Networks}}
  \vspace{0.5em}
  \vspace{1em}
  \textsc{\large CMU 11441/11741: Machine Learning with Graphs} \\
  Due date: 11/07/2024, 11:59 PM EST
  
  \href{https://github.com/Shengyu-Feng/mlwg_f24_hw4}{GitHub repository for the assignment}
  \vspace{0.5em}

\end{center}

\section*{Instructions}
\begin{itemize}
\item \textbf{Allowed libraries:} This assignment involves implementing graph convolutional networks. You are \textbf{not} allowed to use any libraries that implement GCNs out of the box (like Pytorch-geometric).
It is allowed to use autodiff libraries like Pytorch/Tensorflow. We highly recommend using Python + Pytorch for this assignment.

\item \textbf{Getting feedback}:
You can create a \textbf{private} fork of the repository on GitHub and add the TAs as collaborators (usernames: Shengyu-Feng, RifleZhang). This might help you in asking questions without having to copy-paste your code on piazza (you can just reference Github code/copy permalink). You can use these instructions or just copy-paste the code into a new repository.

\item \textbf{Posting your solutions online}:
As with all the other assignments, please do not share your solutions publicly.

\item \textbf{Statement of Assurance}

\begin{enumerate}
    \item Did you receive any help whatsoever from anyone in solving this assignment?
    \item Did you give any help whatsoever to anyone in solving this assignment? 
    \item Did you find or come across code that implements any part of this assignment?
\end{enumerate}
\end{itemize}
